---
title: 'QTS data: Spiritual curiosity'
subtitle: 'Last updated 2018-04-12'
output:
  html_notebook: 
    toc: true
  html_document:
    df_print: paged
  pdf_document: default
---

```{r, include = F}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r, include = F}
# load packages
library(readxl)
library(tidyverse)
library(rms)
library(knitr)
library(kableExtra)

# run setup script
source("/Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_qts/scripts/setup_qts_kw.R")

# run data wrangling script
source("/Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_qts/scripts/wrangling_qts_kw.R")

# set key
key <- key_sc
```

This is a first-pass exploration of the QTS data for the "Spiritual curiosity" interview.

# Prayer

```{r, fig.width = 3, fig.asp = 1}
custom_histo("prayfreqmin")
```

```{r, fig.width = 3, fig.asp = 1}
custom_histo("praysilly")
```

```{r, fig.width = 3, fig.asp = 1}
custom_histo("prayprepbody")
custom_histo("prayprepmind")
custom_histo("puremindmovethoughts")
```

# Tongues

```{r, fig.width = 3, fig.asp = 1}
custom_histo("tongues")
```

# Personal communication with God*

## via other people

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godviapeople")
custom_histo("godviapeople_freq")
```

## via scripture

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godviascript")
custom_histo("godviascript_freq")
```

## via God* speaking in your mind

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godviamind")
custom_histo("godviamind_freq")
```

## Qualities of the voice of God*

### you can be mistaken

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godvoxmistaken") 
```

### strong

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godvoxstrong")
```

### a voice out loud

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godvoxaloud")
custom_histo("godvoxaloud_outsidehead")
custom_histo("godvoxaloud_withears")
custom_histo("godvoxaloud_turnhead")
custom_histo("godvoxaloud_waking")
custom_histo("godvoxaloud_freq")
custom_histo("godvoxaloud_judge")
```

# via pictures

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godcommpics")
custom_histo("godcommpics_freq")
```

## via visions

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godviavisions")
custom_histo("godviavisions_outsidehead")
custom_histo("godviavisions_witheyes")
custom_histo("godviavisions_waking")
custom_histo("godviavisions_freq")
custom_histo("godviavisions_judge")
```

## via dreams

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godviadreams")
custom_histo("godviadreams_freq")
```

# via knowing

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godguideviaknowing")
custom_histo("godguideviaknowing_freq")
```

## via the body

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godsenseplaceinbody")
custom_histo("godsenseplaceinbody_loc")
custom_histo("godviabodyexperiences")
```

## via touch

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godviatouch")
custom_histo("godviatouch_realtouch")
custom_histo("godviatouch_waking")
custom_histo("godviatouch_freq")
custom_histo("godviatouch_judge")
```

## via smell

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godviasmell")
custom_histo("godviasmell_realsmell")
custom_histo("godviasmell_waking")
custom_histo("godviasmell_freq")
custom_histo("godviasmell_judge")
```

## ways of feeling beyond the everyday

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godexpviaawe")
custom_histo("godexpviaawe_freq")
custom_histo("godexpviaawe_freqcombo")
```

# Presence of God*

## moment of confirmation

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godconfirm")
```

## tangibility

```{r, fig.width = 3, fig.asp = 1}
custom_histo("neartangiblegod")
custom_histo("neartangiblegod_freq")
custom_histo("neartangiblegod_judge")
```

## other presences

```{r, fig.width = 3, fig.asp = 1}
custom_histo("presencenotgod")
custom_histo("presencenotgod_freq")
custom_histo("presencenotgod_judge")
```

## presence of demons

```{r, fig.width = 3, fig.asp = 1}
custom_histo("presencedemon")
custom_histo("presencedemon_freq")
custom_histo("presencedemon_judge")
```

## another being entering the body

```{r, fig.width = 3, fig.asp = 1}
custom_histo("beingentbody")
custom_histo("beingentbody_freq")
custom_histo("beingentbody_judge")
```

## other entities

```{r, fig.width = 3, fig.asp = 1}
custom_histo("seehearnotgod")
custom_histo("seehearnotgod_judge")
```

## white lights

```{r, fig.width = 3, fig.asp = 1}
custom_histo("whitelight")
custom_histo("whitelight_judge")
```

# Experiences

## trembling & shaking

```{r, fig.width = 3, fig.asp = 1}
custom_histo("whitelight_judge")
custom_histo("trmblshakespirtpwr_freq")
```

## rush of power

```{r, fig.width = 3, fig.asp = 1}
custom_histo("rushofspiritpwr")
custom_histo("rushofspiritpwr_freq")
```

## intense emotion

```{r, fig.width = 3, fig.asp = 1}
custom_histo("intenseemospiritpwr")
custom_histo("intenseemospiritpwr_freq")
```

## time slowing

```{r, fig.width = 3, fig.asp = 1}
custom_histo("timeslowpray")
custom_histo("timeslowpray_freq")
```

## out of body

```{r, fig.width = 3, fig.asp = 1}
custom_histo("mindspiritexitbody")
custom_histo("mindspiritexitbody_freq")
```

## human shape-shifting

```{r, fig.width = 3, fig.asp = 1}
custom_histo("humanshapeshift")
```

## other encounters with spirit beings

```{r, fig.width = 3, fig.asp = 1}
custom_histo("spiritbeingencounter")
custom_histo("spiritbeingencounter_judge")
```

## sleep paralysis

```{r, fig.width = 3, fig.asp = 1}
custom_histo("sleepparalysis")
custom_histo("sleepparalysis_freq")
```

## sleep habits

```{r, fig.width = 3, fig.asp = 1}
custom_histo("sleephabit")
```

# Voices

## hearing a voice when you're alone

```{r, fig.width = 3, fig.asp = 1}
custom_histo("voxwhenalone")
custom_histo("voxwhenalone_outsidehead")
custom_histo("voxwhenalone_withears")
custom_histo("voxwhenalone_turnhead")
custom_histo("voxwhenalone_waking")
custom_histo("voxwhenalone_freq")
custom_histo("voxwhenalone_judge")
```

## seeing something out of the corner of your eye

```{r, fig.width = 3, fig.asp = 1}
custom_histo("seethingscornereye")
custom_histo("seethingscornereye_outsidehead")
custom_histo("seethingscornereye_witheyes")
custom_histo("seethingscornereye_waking")
custom_histo("seethingscornereye_freq")
custom_histo("seethingscornereye_judge")
```

# Skepticism, doubt, spiritual growth

## others' doubt

```{r, fig.width = 3, fig.asp = 1}
custom_histo("othergodnotreal")
```

## own doubt

```{r, fig.width = 3, fig.asp = 1}
custom_histo("selfunsuregodreal")
custom_histo("goddoubt")
```

## spiritual growth

```{r, fig.width = 3, fig.asp = 1}
custom_histo("goddoubtdisclose")
custom_histo("morequesmoreanswr")
custom_histo("doubtimpttogrowth")
custom_histo("growcomfresolvdoubt")
custom_histo("deepquesdefanswr")
```

# Researcher meta-judgments

## of unusual experiences (by sensory modality)

```{r, fig.width = 3, fig.asp = 1}
custom_histo("unusualexphearing_judge")
custom_histo("unusualexpseeing_judge")
custom_histo("unusualexptouch_judge")
custom_histo("unusualexpgod_judge")
custom_histo("unusualexpentity_judge")
```

## of quality of responses

```{r, fig.width = 3, fig.asp = 1}
custom_histo("trueanswers_judge")
custom_histo("falseanswers_judge")
```

