---
title: 'QTS data: Spiritual curiosity'
subtitle: 'Last updated 2018-04-12'
output:
  html_notebook: 
    toc: true
  html_document:
    df_print: paged
  pdf_document: default
---

```{r, include = F}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r, include = F}
# load packages
library(readxl)
library(tidyverse)
library(rms)
library(knitr)
library(kableExtra)

# run setup script
source("/Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_qts/scripts/setup_qts_kw.R")

# run data wrangling script
source("/Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_qts/scripts/wrangling_qts_kw.R")

# run categorization script
source("/Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_qts/scripts/categories_qts_kw.R")

# set key
key <- key_sc
```

This is a first-pass exploration of the QTS data for the "Spiritual curiosity" interview.

# Prayer

```{r, fig.width = 3, fig.asp = 1}
custom_histo("prayfreqmin")
```

```{r, fig.width = 3, fig.asp = 1}
custom_histo("praysilly")
```

```{r, fig.width = 3, fig.asp = 1}
custom_histo("prayprepbody")
custom_histo("prayprepmind")
custom_histo("puremindmovethoughts")
```

# Tongues

```{r, fig.width = 3, fig.asp = 1}
custom_histo("tongues")
```

# Personal communication with God*

## via other people

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godviapeople")
custom_histo("godviapeople_freq")
```

## via scripture

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godviascript")
custom_histo("godviascript_freq")
```

## via God* speaking in your mind

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godviamind")
custom_histo("godviamind_freq")
```

## Qualities of the voice of God*

### you can be mistaken

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godvoxmistaken") 
```

### strong

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godvoxstrong")
```

### a voice out loud

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godvoxaloud")
custom_histo("godvoxaloud_outsidehead")
custom_histo("godvoxaloud_withears")
custom_histo("godvoxaloud_turnhead")
custom_histo("godvoxaloud_waking")
custom_histo("godvoxaloud_freq")
custom_histo("godvoxaloud_judge")
```

# via pictures

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godcommpics")
custom_histo("godcommpics_freq")
```

## via visions

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godviavisions")
custom_histo("godviavisions_outsidehead")
custom_histo("godviavisions_witheyes")
custom_histo("godviavisions_waking")
custom_histo("godviavisions_freq")
custom_histo("godviavisions_judge")
```

## via dreams

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godviadreams")
custom_histo("godviadreams_freq")
```

# via knowing

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godguideviaknowing")
custom_histo("godguideviaknowing_freq")
```

## via the body

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godsenseplaceinbody")
custom_histo("godsenseplaceinbody_loc")
custom_histo("godviabodyexperiences")
```

## via touch

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godviatouch")
custom_histo("godviatouch_realtouch")
custom_histo("godviatouch_waking")
custom_histo("godviatouch_freq")
custom_histo("godviatouch_judge")
```

## via smell

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godviasmell")
custom_histo("godviasmell_realsmell")
custom_histo("godviasmell_waking")
custom_histo("godviasmell_freq")
custom_histo("godviasmell_judge")
```

## ways of feeling beyond the everyday

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godexpviaawe")
custom_histo("godexpviaawe_freq")
custom_histo("godexpviaawe_freqcombo")
```

# Presence of God*

## moment of confirmation

```{r, fig.width = 3, fig.asp = 1}
custom_histo("godconfirm")
```

## tangibility

```{r, fig.width = 3, fig.asp = 1}
custom_histo("neartangiblegod")
custom_histo("neartangiblegod_freq")
custom_histo("neartangiblegod_judge")
```

## other presences

```{r, fig.width = 3, fig.asp = 1}
custom_histo("presencenotgod")
custom_histo("presencenotgod_freq")
custom_histo("presencenotgod_judge")
```

## presence of demons

```{r, fig.width = 3, fig.asp = 1}
custom_histo("presencedemon")
custom_histo("presencedemon_freq")
custom_histo("presencedemon_judge")
```

## another being entering the body

```{r, fig.width = 3, fig.asp = 1}
custom_histo("beingentbody")
custom_histo("beingentbody_freq")
custom_histo("beingentbody_judge")
```

## other entities

```{r, fig.width = 3, fig.asp = 1}
custom_histo("seehearnotgod")
custom_histo("seehearnotgod_judge")
```

## white lights

```{r, fig.width = 3, fig.asp = 1}
custom_histo("whitelight")
custom_histo("whitelight_judge")
```

# Experiences

## trembling & shaking

```{r, fig.width = 3, fig.asp = 1}
custom_histo("whitelight_judge")
custom_histo("trmblshakespirtpwr_freq")
```

## rush of power

```{r, fig.width = 3, fig.asp = 1}
custom_histo("rushofspiritpwr")
custom_histo("rushofspiritpwr_freq")
```

## intense emotion

```{r, fig.width = 3, fig.asp = 1}
custom_histo("intenseemospiritpwr")
custom_histo("intenseemospiritpwr_freq")
```

## time slowing

```{r, fig.width = 3, fig.asp = 1}
custom_histo("timeslowpray")
custom_histo("timeslowpray_freq")
```

## out of body

```{r, fig.width = 3, fig.asp = 1}
custom_histo("mindspiritexitbody")
custom_histo("mindspiritexitbody_freq")
```

## human shape-shifting

```{r, fig.width = 3, fig.asp = 1}
custom_histo("humanshapeshift")
```

## other encounters with spirit beings

```{r, fig.width = 3, fig.asp = 1}
custom_histo("spiritbeingencounter")
custom_histo("spiritbeingencounter_judge")
```

## sleep paralysis

```{r, fig.width = 3, fig.asp = 1}
custom_histo("sleepparalysis")
custom_histo("sleepparalysis_freq")
```

## sleep habits

```{r, fig.width = 3, fig.asp = 1}
custom_histo("sleephabit")
```

# Voices

## hearing a voice when you're alone

```{r, fig.width = 3, fig.asp = 1}
custom_histo("voxwhenalone")
custom_histo("voxwhenalone_outsidehead")
custom_histo("voxwhenalone_withears")
custom_histo("voxwhenalone_turnhead")
custom_histo("voxwhenalone_waking")
custom_histo("voxwhenalone_freq")
custom_histo("voxwhenalone_judge")
```

## seeing something out of the corner of your eye

```{r, fig.width = 3, fig.asp = 1}
custom_histo("seethingscornereye")
custom_histo("seethingscornereye_outsidehead")
custom_histo("seethingscornereye_witheyes")
custom_histo("seethingscornereye_waking")
custom_histo("seethingscornereye_freq")
custom_histo("seethingscornereye_judge")
```

# Skepticism, doubt, spiritual growth

## others' doubt

```{r, fig.width = 3, fig.asp = 1}
custom_histo("othergodnotreal")
```

## own doubt

```{r, fig.width = 3, fig.asp = 1}
custom_histo("selfunsuregodreal")
custom_histo("goddoubt")
```

## spiritual growth

```{r, fig.width = 3, fig.asp = 1}
custom_histo("goddoubtdisclose")
custom_histo("morequesmoreanswr")
custom_histo("doubtimpttogrowth")
custom_histo("growcomfresolvdoubt")
custom_histo("deepquesdefanswr")
```

# Researcher meta-judgments

## of unusual experiences (by sensory modality)

```{r, fig.width = 3, fig.asp = 1}
custom_histo("unusualexphearing_judge")
custom_histo("unusualexpseeing_judge")
custom_histo("unusualexptouch_judge")
custom_histo("unusualexpgod_judge")
custom_histo("unusualexpentity_judge")
```

## of quality of responses

```{r, fig.width = 3, fig.asp = 1}
custom_histo("trueanswers_judge")
custom_histo("falseanswers_judge")
```

# Aggregating all spiritual experiences together

**Questions ID'd by Josh on 2018-04-12**

```{r, fig.width = 4, fig.asp = 0.6}
d_spirit %>%
  distinct(country, researcher, urban_rural, charismatic_local, 
           subject_name, spex_score) %>%
  group_by(country, researcher, urban_rural, charismatic_local) %>%
  do(data.frame(rbind(smean.cl.boot(.$spex_score)))) %>%
  ungroup() %>%
  ggplot(aes(x = interaction(charismatic_local, urban_rural), 
             y = Mean, color = researcher)) +
  facet_grid(~ country, scales = "free", space = "free") +
  geom_pointrange(aes(ymin = Lower, ymax = Upper)) +
  geom_text(aes(label = round(Mean, 1), y = Lower), 
            color = "black", nudge_y = -2, size = 2) +
  scale_color_manual(values = custom_pal) +
  scale_y_continuous(limits = c(0, 24)) +
  labs(title = "Mean responses: total 'spiritual experience' score (range: 0-24)",
       subtitle = "Error bars are 95% confidence intervals",
       x = "Score",
       y = "Count",
       color = "Researcher") +
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  guides(color = guide_legend(ncol = 6, byrow = TRUE))
```

```{r, fig.width = 3, fig.asp = 1}
d_spirit %>%
  filter(!is.na(spex_score)) %>%
  distinct(country, researcher, urban_rural, charismatic_local, 
           subject_name, spex_score) %>%
  group_by(country, urban_rural, charismatic_local) %>%
  mutate(med_abs = median(spex_score, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = spex_score, fill = researcher)) +
  facet_grid(urban_rural ~ charismatic_local ~ country) +
  geom_vline(aes(xintercept = med_abs), lty = 2, size = 0.2) +
  geom_histogram(binwidth = 0.2 * (max(d_spirit$spex_score, na.rm = T) -
                                     min(d_spirit$spex_score, na.rm = T) + 1)) +
  geom_text(data = . %>% 
              distinct(country, urban_rural, charismatic_local, med_abs),
            aes(x = 0, y = 12, fill = NULL,
                label = paste0("Median: ", med_abs)),
            size = 2, hjust = 0) +
  scale_fill_manual(values = custom_pal) +
  scale_alpha_discrete(guide = "none", range = c(0.5, 1)) +
  scale_x_continuous(limits = c(0, 24), breaks = seq(0, 100, 5)) +
  labs(title = paste("Distribution of responses:", "spex_score"),
       subtitle = "Sum of all 'spiritual experience' items (range: 0-24)",
       x = "Score",
       y = "Count",
       fill = "Researcher") +
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  guides(fill = guide_legend(ncol = 6, byrow = TRUE))
```