---
title: 'QTS data: Thinking about thinking'
subtitle: 'Last updated 2018-04-09'
output:
  html_notebook: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r, include = F}
knitr::opts_chunk$set(echo = FALSE, message = FALSE)
```

```{r, include = F}
# load packages
library(readxl)
library(tidyverse)
library(rms)
library(knitr)
library(kableExtra)

# run setup script
source("/Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_qts/scripts/setup_qts_kw.R")

# run data wrangling script
source("/Users/kweisman/Documents/Research (Stanford)/Projects/Templeton Grant/DATA WRANGLING/templeton_qts/scripts/wrangling_qts_kw.R")

# set key
key <- key_tat
```

This is a first-pass exploration of the QTS data for the "Thinking about thinking" interview.

# Absorption

## ... overall summary score

*NOTE: Nikki has concerns that this might not deal adequately with people who skipped questions.**

```{r, fig.width = 3, fig.asp = 1}
d %>%
  filter(!is.na(abs_score)) %>%
  group_by(country, urban_rural, charismatic_local) %>%
  mutate(med_abs = median(abs_score, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = abs_score, fill = researcher)) +
  facet_grid(urban_rural ~ charismatic_local ~ country) +
  geom_vline(aes(xintercept = med_abs), lty = 2, size = 0.2) +
  geom_histogram(bins = 0.2 * (max(d$abs_score, na.rm = T) -
                                 min(d$abs_score, na.rm = T) + 1)) +
  geom_text(data = . %>% 
              distinct(country, urban_rural, charismatic_local, med_abs),
            aes(x = 0, y = 12, fill = NULL,
                label = paste0("Median: ", med_abs)),
            size = 2, hjust = 0) +
  scale_fill_manual(values = custom_pal) +
  scale_alpha_discrete(guide = "none", range = c(0.5, 1)) +
  labs(title = paste("Distribution of responses:", "abs_score"),
       subtitle = "Sum of all absorption items (range: 0-34)",
       x = "Score",
       y = "Count",
       fill = "Researcher") +
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  guides(fill = guide_legend(ncol = 6, byrow = TRUE))
```

## ... individual 'absorption' items

```{r, fig.width = 3, fig.asp = 1}
custom_histo("childexp_abs")
custom_histo("forgetsurrounding_abs")
custom_histo("poeticlanguage_abs")
custom_histo("starepicture_abs")
```

```{r, fig.width = 3, fig.asp = 1}
custom_histo("mindenvelopworld_abs")
custom_histo("cloudshapes_abs")
custom_histo("vividdaydream_abs")
custom_histo("mysticalexp_abs")
```

```{r, fig.width = 3, fig.asp = 1}
custom_histo("stepoutsidemyself_abs")
custom_histo("textures_abs")
custom_histo("doublyreal_abs")
custom_histo("caughtupinmusic_abs")
```

```{r, fig.width = 3, fig.asp = 1}
custom_histo("heavybody_abs")
custom_histo("sensepresence_abs")
custom_histo("woodfireimagine_abs")
custom_histo("immersednature_abs")
```

```{r, fig.width = 3, fig.asp = 1}
custom_histo("colormeaning_abs")
custom_histo("wanderthoughtstask_abs")
custom_histo("clearpastexp_abs")
custom_histo("meaninglesstoothers_abs")
```

```{r, fig.width = 3, fig.asp = 1}
custom_histo("actinginplay_abs")
custom_histo("visualthoughts_abs")
custom_histo("delightsmallthings_abs")
custom_histo("organmusic_abs")
```

```{r, fig.width = 3, fig.asp = 1}
custom_histo("changenoise_abs")
custom_histo("vividsmellmemories_abs")
custom_histo("synesthesiasound_abs")
custom_histo("predictwords_abs")
```

```{r, fig.width = 3, fig.asp = 1}
custom_histo("physicalmemories_abs")
custom_histo("fascinatingvoice_abs")
custom_histo("invisiblepresence_abs")
custom_histo("sponthoughtsimages_abs")
```

```{r, fig.width = 3, fig.asp = 1}
custom_histo("synesthesiasmell_abs")
custom_histo("emosunset_abs")
```

# Mental causation

## ... ANGER

## ... mechanism unspecified

```{r, fig.width = 3, fig.asp = 1}
custom_histo("hurtwfeelings_anger")
custom_histo("hurtwthoughts_anger")
```

## ... health

```{r, fig.width = 3, fig.asp = 1}
custom_histo("healtheffectbyproxy_anger")
```

## ... via spirit mediation

```{r, fig.width = 3, fig.asp = 1}
custom_histo("hurtviaspirit_anger")
custom_histo("awarespirit_anger")
custom_histo("healtheffectself_anger")
```

## ... regulation

```{r, fig.width = 3, fig.asp = 1}
custom_histo("stopemo_anger")
custom_histo("removethoughts_anger")
custom_histo("controlemo_anger")
custom_histo("shouldcontrol_anger")
custom_histo("trycontrol_anger")
```

## ... sharing

```{r, fig.width = 3, fig.asp = 1}
custom_histo("disclose_anger")
```

## ... CARING

## ... mechanism unspecified

```{r, fig.width = 3, fig.asp = 1}
custom_histo("helpwthoughts_caring")
```

## ... via spirit mediation

```{r, fig.width = 3, fig.asp = 1}
custom_histo("helpviaspirit_caring")
custom_histo("awarespirit_caring")
custom_histo("healtheffectself_caring")
```

## ... health

```{r, fig.width = 3, fig.asp = 1}
custom_histo("healtheffectbyproxy_caring")
```


## ... regulation

```{r, fig.width = 3, fig.asp = 1}
custom_histo("toomuch_caring")
```

## ... sharing

```{r, fig.width = 3, fig.asp = 1}
custom_histo("disclose_caring")
```

## ... ENVY

## ... mechanism unspecified

```{r, fig.width = 3, fig.asp = 1}
custom_histo("hurtwfeelings_envy")
custom_histo("hurtwthoughts_envy")
```

## ... health

```{r, fig.width = 3, fig.asp = 1}
custom_histo("healtheffectself_envy")
```

## ... via spirit mediation

```{r, fig.width = 3, fig.asp = 1}
custom_histo("hurtviaspirit_envy")
custom_histo("awarespirit_envy")
custom_histo("disclose_envy")
```


## ... sharing

```{r, fig.width = 3, fig.asp = 1}
custom_histo("disclose_envy")
```

## general

```{r, fig.width = 3, fig.asp = 1}
custom_histo("spiritsusethoughtsharm")
custom_histo("witchcraft_judge")
```

# Interiority

## ... sharing

```{r, fig.width = 3, fig.asp = 1}
custom_histo("socialharmony")
custom_histo("happyface")
custom_histo("controlface")
```

## ... understanding/reflection

```{r, fig.width = 3, fig.asp = 1}
custom_histo("understandthoughts")
```

## ... danger

```{r, fig.width = 3, fig.asp = 1}
custom_histo("sharingdangerous")
```

## ... talking

```{r, fig.width = 3, fig.asp = 1}
custom_histo("talkabtfeelings")
custom_histo("sharefeelingshere")
```

## general

```{r, fig.width = 3, fig.asp = 1}
custom_histo("sharethought_judge")
custom_histo("controlbody_judge")
```

# Imagination

## ... child vignettes 

```{r, fig.width = 3, fig.asp = 1}
custom_histo("choochoo_imagine")
custom_histo("choochoo_encourage")
```

```{r, fig.width = 3, fig.asp = 1}
custom_histo("teddydinner_imagine")
custom_histo("teddydinner_encourage")
```

```{r, fig.width = 3, fig.asp = 1}
custom_histo("invisiblefriend_imagine")
custom_histo("invisiblefriend_encourage")
```


```{r, fig.width = 3, fig.asp = 1}
custom_histo("childsplayopinion_imagine")
```

```{r, fig.width = 3, fig.asp = 1}
custom_histo("adultsplaywchild_imagine")
custom_histo("adultsplaywchild_encourage")
```

```{r, fig.width = 3, fig.asp = 1}
custom_histo("adultsscarekids_imagine")
custom_histo("adultscarekids_encourage")
```

## ... cup of tea for God

```{r, fig.width = 3, fig.asp = 1}
custom_histo("teaforgod_imagine")
custom_histo("teaforgod_encourage")
custom_histo("teaforgod_outcome")
```

## ... general

```{r, fig.width = 3, fig.asp = 1}
custom_histo("adultsimagineimpossible_import")
custom_histo("adultsimaginepossible_import")
```

```{r, fig.width = 3, fig.asp = 1}
custom_histo("magicalthinking")
```

# SCID

## ... summary score

```{r, fig.width = 3, fig.asp = 1}
d %>%
  select(subject_name, country, researcher, urban_rural, charismatic_local, 
         ends_with("_scid")) %>%
  gather(question, response, ends_with("_scid")) %>%
  mutate(response = as.numeric(factor(response,
                                      levels = c("Not present",
                                                 "Present but uncertain",
                                                 "Persuaded of issue")))) %>%
  group_by(country, researcher, urban_rural, charismatic_local, subject_name) %>%
  summarise(scid_score = sum(response, na.rm = T)) %>%
  ungroup() %>%
  filter(!is.na(scid_score)) %>%
  group_by(country, researcher, urban_rural, charismatic_local) %>%
  mutate(med_scid = median(scid_score, na.rm = T)) %>%
  ungroup() %>%
  ggplot(aes(x = scid_score, fill = researcher)) +
  facet_grid(urban_rural ~ charismatic_local ~ country) +
  geom_vline(aes(xintercept = med_scid), lty = 2, size = 0.2) +
  geom_histogram(binwidth = 1) +
  geom_text(data = . %>% 
              distinct(country, urban_rural, charismatic_local, med_scid),
            aes(x = 0, y = 20, fill = NULL,
                label = paste0("Median: ", med_scid)),
            size = 2, hjust = 0) +
  scale_fill_manual(values = custom_pal) +
  scale_alpha_discrete(guide = "none", range = c(0.5, 1)) +
  labs(title = paste("Distribution of responses:", "scid_score"),
       subtitle = "Sum of all SCID items (range: 0-16, for now)",
       x = "Score",
       y = "Count",
       fill = "Researcher") +
  theme_bw() +
  theme(legend.position = "top",
        axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  guides(fill = guide_legend(ncol = 6, byrow = TRUE))
```

## ... individual items

```{r, fig.width = 3, fig.asp = 1}
custom_histo("specialmessage_scid")
custom_histo("specialmessagenotgod_scid")
custom_histo("threatening_scid")
custom_histo("importantperson_scid")
```

```{r, fig.width = 3, fig.asp = 1}
custom_histo("hypochondriasis_scid")
custom_histo("somaticshift_scid")
custom_histo("terribleact_scid")
custom_histo("alienthought_scid")
```

```{r, fig.width = 3, fig.asp = 1, include = F}
# custom_histo("thoughtstaken_scid")
# custom_histo("thoughtsbroadcast_scid")
# custom_histo("hearthings_scid")
# custom_histo("hearthingsfreq_scid")
# custom_histo("hearthingscontent_scid")
# custom_histo("hospitalhx_scid")
```

